### 2018-05-18 paper/paper.tex

In an evaluative adjective sentence (EAS) like (\ref{f}), the
evaluative adjective {\em stupid} subcategorizes for a non-pleonastic subject noun
phrase ({\em Feynman}) and a {\em to-}infinitive ({\em to
dance on the table}); the subject of {\em stupid} is the understood subject of the {\em to-}infinitive (e.g., \citealt{wilkinson70, norrick78,barker02,kertz2010}). Two contents of EASs that this paper is concerned with are the `prejacent' and the `evaluation': in (\ref{f}), the prejacent is that Feynman danced on the table and the evaluation is that 
Feynman dancing on the table was stupid.\footnote{This paper ignores the subject-related presuppositions discussed in \citealt{barker02}.}

@@

\begin{exe}
\ex\label{nat} \citealt[235]{karttunen-etal2014}
\begin{xlist}
\ex I wasn't \fbox{fortunate} to live extremely close to my Mom and Dad for most of my adult life. The closest was when I was in Denver and they were in Garden City, KS.

@@

\ex  Now I knew someone was in the junkyard and the cold wind was
carrying the cries. I wasn't \fbox{stupid} to go stumbling through the
junkyard in the dark and get hurt.

@@

Examples like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with
binding: if the prejacent was added to the common ground,
(\ref{nat}b) would mean that the speaker knew that someone was in the
junkyard, that they stumbled through the junkyard and got hurt, and that
the speaker does not consider these actions stupid (perhaps because these actions
led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with
binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. From this perspective, the cues to the projectivity of the prejacent identified in this paper may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. The second problem with presuppositional analyses of the prejacent, however, is not addressed by considering plausibility.}

@@

According to \citepos{barker02} dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25). In other words, only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated under negation, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. In other words, only those worlds remain in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as discussed above, this is not what (\ref{nat}b) is understood to mean. In sum, analyses of EASs according to which the prejacent is a presupposition do not account for examples like (\ref{nat}) in which the prejacent is interpreted in the scope of negation, but the evaluation is not. In sum, analyses of EAS according to which the prejacent is a presupposition do not account for the interpretation of examples like (\ref{nat}).

@@

\citepos{karttunen-etal2014} analysis improves over previous analyses because it is able to derive both attested interpretations. But the analysis comes at a cost: first, evaluative adjectives are systematically ambiguous, and, second, as we argue in section \ref{s3}, it misses out on an empirical generalization about how common ground information  influences the interpretation of EASs. In this paper, we develop an analysis of EASs that accounts for the two interpretations with a single lexical entry for evaluative adjectives. The crux of the analysis is that evaluative adjectives do not lexically specify that the prejacent is a presupposition. In section \ref{s2}, we show, based on a study of naturally occurring NEASs, that the prejacent is not highly projective. We take this to provide empirical support for not analyzing the prejacent as a lexically-specified presupposition. In section \ref{s3}, we present an analysis of EASs according to which the projectivity of the prejacent of an utterance in which the evaluative adjective is embedded under an entailment-canceling operator is predicted by the extent to which the prejacent is at-issue with respect to the Discourse Question addressed by the utterance. We present empirical evidence for three predictions of the analysis in section \ref{s4} and discuss two open issues in section \ref{s5}. The paper concludes in section \ref{s6}.

\section{The projectivity of the prejacent in naturally occurring examples}\label{s2}

\citet{karttunen-etal2014} provided naturally occurring examples that showed that the prejacent of NEASs need not project. The goal of the study we present in this section was to more systematically explore how projective the prejacent is in naturally occurring NEAS. Following \citealt{tbd-variability}, we assume that projectivity is a gradient property of utterance content: the more the speaker or author of the utterance is taken to be committed to the truth of an utterance content, the more projective the content is. To explore the projectivity of the prejacent, native speakers of American English were presented with naturally occurring NEAS and asked to rate the projectivity of the prejacent.\footnote{\label{f-git}The
materials, data and the R code for generating the figures and analyses
of the corpus study and the experiments reported on in this paper are available at
\url{https://github.com/judith-tonhauser/evaluative-adjectives}.}

@@

\paragraph{Materials} Using the online interface of the EnTenTen corpus,\footnote{The EnTenTen 2012 corpus has 11,191,860,036 words
(\url{www.sketchengine.co.uk}, \citealt{ententen}).} we searched for NEASs that matched one of the strings in (\ref{string}) where ADJ was one of the following 10 evaluative adjectives that have been analyzed as presupposing the prejacent (e.g., \citealt{norrick78,karttunen-etal2014}): {\em stupid, smart, wise,
fortunate, lucky, brave, polite, mean, foolish} and {\em rude}.

@@

Each target stimulus was attributed to an author who was identified by name, as shown for the sample stimuli in (\ref{target1}). (The evaluative adjective was not framed when the stimuli were presented to the participants.) As shown in the `Question to participants' presented with each stimulus in (\ref{target1}), we used the `certain that' diagnostic for projectivity to assess whether participants took the author to be committed to the prejacent, i.e., whether the prejacent projects over negation. For other applications of the `certain that' diagnostic for projection see \citealt{tonhauser-salt26,djaerv-bacovcin-salt27,stevens-etal2017} and \citealt{tbd-variability}. In these `Questions to participants', the prejacent was realized as the finite complement clause of {\em certain}. The tense of the finite clause that realized the prejacent was determined by the temporal and aspectual properties of the
NEAS: it was past tense for past tense NEAS, as in (\ref{target1}a), and future tense for future tense NEAS, as in (\ref{target1}b); for non-past tense NEAS, the finite clause that realized the prejacent was realized in the non-past tense if the eventuality denoted by the prejacent was
stative, as in (\ref{target1}c), and a disjunction of a past tense and a future tense verb if the prejacent was eventive, as in (\ref{target1}d).

@@

\ex Shawn: Mr. Anderson --  Just discovered your
site on The 1939-40 New York World's Fair. It brought back a lot of
memories for me. Thanks for the time you spent in constructing this
site. I was not \fbox{fortunate} to visit the 1939-40 World's Fair but I
had an uncle who did.
\\ Question to participants: Is Shawn certain that he visited the 1939-40 World's Fair?

\ex Megan: For sure P1 will not be \fbox{stupid} to create a WiMAX netbook to allow YTL or AMAX customers to use.
\\ Question to participants: Is Megan certain that P1 will create a WiMAX netbook to allow YTL or AMAX customers to use?

\ex Frank: God offers Hope to Hispanics! In His pages are solutions to every immigration problem. God loves citizens and immigrants equally. His solutions are for all of us. They are practical. They work. He is not \fbox{stupid} to think so.
\\ Question to participants: Is Frank certain that God thinks that his solutions work?

\ex Anna: The flight attendants are not \fbox{wise} to invoke the specter
of a strike. \\ Question to participants: Is Anna certain that the
flight attendants invoked or will invoke the specter of a strike?

@@

\begin{figure}[h!]
\begin{center}
\fbox{\includegraphics[width=10cm]{figures/f-corpus-trial}}
\end{center}
\caption{A sample trial in the corpus study}\label{f-corpus-trial}
\end{figure}

@@

\paragraph{Data exclusion} The responses from 6 participants who did not self-identify as native speakers of American English were excluded. 28 participants gave a rating higher than 3 to the control stimulus in (\ref{cntrl}a), for which we hypothesized that participants would not take the speaker to be committed to the relevant content, or a rating lower than 5 to the control stimulus in (\ref{cntrl}b), for which we hypothesized that participants would take the speaker to be committed to the relevant content. The data from these 28 participants were also excluded, leaving data from 226 participants (ages: 18-83; mean: 35).

@@

There were 26-32 certainty ratings for each of the 59 NEAS (mean: 28.5), except for the five NEASs that appeared on two lists, for which there were 52-58 certainty ratings each (mean: 54). We calculated the mean certainty rating of the prejacent of each NEAS: the lowest mean certainty rating was 1.2, the highest was 6.7 and the mean certainty rating overall was 3.2. Given that participants gave their ratings on a 7-point scale, with the lowest rating (1) indicating that the speaker was not certain about the relevant content and the highest rating (7) indicating that the speaker was certain about the relevant content, this mean certainty rating already suggests that the prejacent of naturally occurring NEAS is not highly projective. Figure \ref{f-corpus} shows the mean certainty ratings of each NEAS by evaluative adjective; darker dots indicate overlapping means. The distribution of mean certainty ratings again suggests that the prejacent of naturally occurring NEAS is projective, but not highly so, and that NEAS in which the prejacent does not project are well-attested in naturally occurring data. These findings provide empirical support for an analysis according to which the prejacent is not lexically specified as a presupposition. \jd{can't they just invoke the `dialect' response here? or did you make sure that each participant saw multiple instances of each adjective, so you can compare whether within subjects ratings differ?}

@@

\includegraphics[width=.7\paperwidth]{../corpus-study/graphs/mean-response-by-item-and-adj}

\caption{Mean certainty rating of 59 naturally occurring NEASs by evaluative adjective. Darker dots indicate overlapping means.\jd{There should be error bars or sth showing the amount of uncertainty around means on this. I couldn't find the code for it or I would have tried sth}}\label{f-corpus}

@@

\ex God offers Hope to Hispanics! In His pages are solutions to every immigration problem. God loves citizens and immigrants equally. His solutions are for all of us. They are practical. They work. He is not \fbox{stupid} to think so. \hfill {\bf [6.3]}

\ex There is no chance a true large scale museum can be built. The federal government cannot take on the humongous legal liability for such a hazardous site. The Google founders are not \fbox{stupid} to take on that liability either. \hfill {\bf [1.9]}

@@

\ex Four months after her last Prolotherapy treatment  Tessie is still
doing great. But what would have happened if she was not
\fbox{fortunate} to be married to Joe? \hfill {\bf [6.4]}

\ex\label{fair}  Mr. Anderson  Just discovered your site on The 1939-40 New York World's Fair. It brought back a lot of memories for me. Thanks for the time you spent in constructing this site. I was not \fbox{fortunate} to visit the 1939-40 World's Fair but I had an uncle who did \hfill {\bf [1.2]}

@@

\ex Not even a 40 foot ladder could reach this roof  so I had to use a boom (bucket) lift. I got a 60' lift for this particular job  and it worked out nicely. I took the above photo while working in the lift. You can see the tiles. They look nice and neat in the photo  but up close  they were riddled with gaps. I spent a great deal of time sealing them. I was lucky to have level and relatively unobstructed ground. I was not \fbox{lucky} to have recent rains and a several ton machine to drive on the soft ground. \hfill {\bf [5.9]}

@@

\ex Alice: Good day. My husband and i were married for four years now but before that he already has a child with his ex gf. We are not \fbox{lucky} to have a child of our own. \hfill {\bf [1.4]}

@@

\begin{xlist} \ex Out east in St. Bernard Parish Chad Blanchard is
hoping he was not \fbox{foolish} to spend his savings on reopening
Charlie's restaurant -- leaving himself with just 15 dollar bills in his
back pocket. \hfill {\bf [5.4]}

@@

\ex Olmert is a dinosaur politician  he will exist for a long time in politics  and therefore will not be \fbox{foolish} to make the same mistake twice. \hfill {\bf [2.1]}

@@

\ex I think Mark Cuban was not \fbox{smart} to let a successful coach go in Avery Johnson. \hfill {\bf [6.7]}

@@

\ex Once you installed this free Notipage webpage monitoring software
then just make your first alert. It's worth mentioning here that the app
will not be \fbox{smart} to keep an eye on web pages that are only easy
to get to by logging in to a site or service.   \hfill {\bf [2.2]}

@@

In sum, our study of naturally occurring NEAS shows that the prejacent is not highly projective. These findings converge with those of \citet{tbd-variability}, who studied the projectivity of a variety of utterance contents and found that the prejacent of (constructed) polar interrogative EASs with {\em stupid} was significantly less projective than the content of the clausal complement of the emotive predicate {\em be annoyed} and the cognitive predicate {\em know}. We take these findings to support an analysis according to which the projectivity of the prejacent is not due to its lexical status as a presupposition but instead derived from the question that the utterance of the EAS is taken to address. This question-based analysis of the projectivity of the prejacent is developed in the next section.

@@

\begin{exe}
\ex\label{ent} Two lexical entailments of unembedded evaluative adjective sentences `NP be{\sc .tense} Adj to VP'\footnote{Some EASs with {\em will} appear to not entail the prejacent: for example, some speakers do not judge (i) to entail that Johnson will take what he can get. We thank David Beaver (p.c.) for this point, which we sidestep here.
\begin{exe}
\exi{(i)} With more teams denying interest in Johnson, he will be \fbox{smart}
to take what he can get. \\ ({\em http://www.sportsworldreport.com/articles/28999/20140407/chris-johnson-rumors-ny-jets-release-mike-goodson-free-agent-signs-dallas-cowboys-demarco-murray-rams-falcons.htm})
\end{exe}}

@@

\ex Generalization: In VPing NP is Adj

@@

\end{xlist}
\end{exe}
By (\ref{ent}), a past tense EAS like (\ref{f}) {\em Feynman was stupid to dance on the table} entails that in dancing on the table Feynman is stupid (the generalization) and that Feynman danced on the table (the prejacent). Likewise, a present tense EAS like the non-negated variant of (\ref{stupid}b) {\em God is stupid to think that his solutions work} entails that in thinking that his solutions work God is stupid (the generalization) and that God thinks that his solutions work (the prejacent). The generalization is timeless and attributes the property denoted by Adj to the referent of the NP relatve to events of the type denoted by the VP. These events may, but need not be, actual: for instance, it does not from the generalization of (\ref{f}) that an event of Feynman dancing on the table took place.

In contrast to the generalization and the prejacent, we do not take the evaluation to be a lexical entailment of EASs (unlike, e.g., \citealt{barker02}). However, for unembedded EASs, the evaluation follows straightforwardly from the lexical entailments. For instance, in (\ref{f}), the evaluation that Feynman was stupid to dance on the table follows from the generalization, that in dancing on the table Feynman is stupid, and the prejacent, that Feynman danced on the table. To preview the proposal: when an EAS is embedded under an entailment-canceling operator, it is not the case that both of the lexical entailments survive as commitments of the speaker. As a consequence, what follows from such EASs differs, thus capturing, as we show below, that the evaluation of such sentences depends on which content projects, i.e., is a commitment of the speaker.

The analysis in (\ref{ent}), according to which the prejacent and the generalization are lexical entailments, predicts that unembedded EASs are judged to be unacceptable if either entailment is false. The examples in (\ref{false}) show that that prediction is borne out. Consider (\ref{false}a), whose prejacent is false and whose generalization is true (under the assumption that anybody, including Kim, being born into poverty is unfortunate): this example is correctly predicted to be unacceptable because the prejacent is false. In (\ref{false}b), on the other hand, the prejacent is true and the generalization is false (under the assumption that it is not the case that anybody, including Sandy, being born into poverty is lucky). This sentence is correctly predicted to be judged to be unacceptable because the generalization is false.

@@

The generalization of an EAS involves the meaning of the (positive) evaluative adjective, whose meaning depends on a contextual standard (e.g., \citealt{kennedy2001}). Our examples in (\ref{false}) appealed to a contextual standard for {\em unfortunate} and {\em lucky} such that any reader would agree that somebody being born into poverty counts as unfortunate and doesn't count as lucky; more elaborately: the degree to which somebody being born into poverty is unfortunate is higher than the contextual standard for {\em unfortunate} and the degree to which somebody being born into poverty is lucky is lower than the contextual standard for {\em lucky}. What follows from the common ground, which we assume includes world knowledge, is that the generalization of (\ref{false}a), that Kim being born into poverty is unfortunate, is true and the generalization of (\ref{false}b), that Sandy being born into poverty is lucky, is false.

The common ground does not always determine whether the generalization of an EAS is true or false. Consider, for instance, the generalization that a particular individual $x$ buying the Xbox 360 Elite is stupid. Whether this generalization is true or false depends on $x$'s personal circumstances, such as how much money they have, whether they are addicted to gaming and shouldn't be tempted any further, or whether the Xbox is a present for somebody else. Common ground information does not suffice to identify whether the generalization is true or false; we refer to such generalizations as `neutral'. As a consequence, when a speaker utters the EAS in (\ref{xbox}), the generalization, that in buying the Xbox 360 Elite the speaker is stupid, is new information that the speaker is committing to as true: the speaker informs the addressee that the degree to which them buying an Xbox 360 Elite is stupid is higher than the contextual standard of {\em stupid} (see also \citealt{barker02} for this point). For other speakers, this generalization may be false, in which case they could not truthfully utter (\ref{xbox}).

@@

\ex
\begin{xlist}
\exi{A:} There were so few tickets for the show! How did Sam get a ticket?

@@

\ex
\begin{xlist}
\exi{A:} Only famous people got a ticket for the show. Luck had nothing to do with it, did it?

@@

\ex
\begin{xlist}
\exi{A:} There were so few tickets for the show! How did Sam get a ticket?

\exi{B:} Sam wasn't smart to buy one the day they went on sale. (Her sister gave her a ticket.)

@@

In this section, we argue that the information structure of an utterance of an EAS provides a cue to the the Discourse Question addressed and, thereby, to the at-issueness of the prejacent.

@@

>>>>

In an evaluative adjective sentence (EAS) like (\ref{f}), the
evaluative adjective {\em stupid} subcategorizes for a non-pleonastic subject noun
phrase ({\em Feynman}) and a {\em to-}infinitive ({\em to
dance on the table}); the subject of the predicate {\em be stupid} is the understood subject of the {\em to-}infinitive (e.g., \citealt{wilkinson70, norrick78,barker02,kertz2010}). Two contents of EASs that this paper is concerned with are the `prejacent' and the `evaluation': in (\ref{f}), the prejacent is that Feynman danced on the table and the evaluation is that 
Feynman dancing on the table was stupid.\footnote{This paper ignores the subject-related presuppositions discussed in \citealt{barker02}.}

@@

\begin{exe}
\ex\label{nat} \citealt[235]{karttunen-etal2014}
\begin{xlist}
\ex I wasn't fortunate to live extremely close to my Mom and Dad for most of my adult life. The closest was when I was in Denver and they were in Garden City, KS.

@@

\ex  Now I knew someone was in the junkyard and the cold wind was
carrying the cries. I wasn't stupid to go stumbling through the
junkyard in the dark and get hurt.

@@

Examples like (\ref{nat}) point to two problems for analyses according to which the prejacent is a presupposition. The first problem concerns the prejacent. In example (\ref{nat}b), globally accommodating the prejacent does not result in a contradiction, uninformativity or problems with
binding: if the prejacent was added to the common ground,
(\ref{nat}b) would mean that the speaker knew that someone was in the
junkyard, that they stumbled through the junkyard and got hurt, and that
the speaker does not consider these actions stupid (perhaps because these actions
led to the person in the junkyard receiving help). Because such an interpretation does not result in a contradiction, uninformativity or problems with
binding, analyses that take the prejacent to be a presupposition incorrectly  predict that the prejacent of (\ref{nat}b) is globally accommodated, i.e., is a commitment of the speaker.\footnote{It may be possible to account for the non-projection of the prejacent on the basis of plausibility considerations: \citealt[162]{vonfintel08}, for instance,  proposed that ``what gets accommodated depends on the best guess of the hearers about what the speaker might have intended as the adjustment to the common ground that would admit the asserted sentence''. From this perspective, the cues to the projectivity of the prejacent identified in this paper may help flesh out the reasoning process that hearers and readers undergo in interpreting EASs. Plausibility considerations do not, however, address the second problem that presuppositional analyses face.}

@@

According to \citepos{barker02} dynamic semantic analysis, the update effect of a NEAS like (\ref{f2}a) is to filter out those worlds in which the contextual standard of {\em stupid} is too high for Feynman's participation in the event of dancing on the table to count as stupid (p.25). In other words, only those worlds remain in which Feynman dancing on the table is not considered stupid. Similarly then, the update effect of (\ref{nat}b), in which the prejacent is locally accommodated under negation, is to filter out those worlds in which the contextual standard of {\em stupid} is too high for the speaker's participation in the event of stumbling through the junkyard to count as stupid. In other words, only those worlds remain in which the speaker does not stumble through the junkyard and in which the speaker stumbling through the junkyard is not stupid. However, as discussed above, this is not what (\ref{nat}b) is understood to mean. In sum, analyses of EASs according to which the prejacent is a presupposition do not account for examples like (\ref{nat}) in which the prejacent is interpreted in the scope of negation, but the evaluation is not.

@@

\citepos{karttunen-etal2014} analysis improves over previous analyses because it is able to derive both attested interpretations. But the analysis comes at a cost: first, evaluative adjectives are systematically ambiguous, and, second, as we argue in section \ref{s3}, it misses out on an empirical generalization about how common ground information  influences the interpretation of EASs. In this paper, we develop an analysis of EASs that accounts for the two interpretations with a single lexical entry for evaluative adjectives. The crux of the analysis is that evaluative adjectives do not lexically specify that the prejacent is a presupposition. In section \ref{s2}, we show, based on a study of naturally occurring NEASs, that the prejacent is not highly projective. We take this to provide empirical support for not analyzing the prejacent as a lexically-specified presupposition. In section \ref{s3}, we present an analysis of EASs according to which the projectivity of the prejacent of an utterance in which the evaluative adjective is embedded under an entailment-canceling operator is predicted by the extent to which the prejacent is at-issue with respect to the Discourse Question addressed by the utterance. We test three predictions of the analysis in section \ref{s4} and discuss two open issues in section \ref{s5}. The paper concludes in section \ref{s6}.

\section{Experiment 1: Projectivity of the prejacent in naturally occurring NEAS}\label{s2}

\citet{karttunen-etal2014} provided naturally occurring examples that showed that the prejacent of NEASs need not project. The goal of the study we present in this section was to more systematically explore how projective the prejacent is in naturally occurring NEAS. Following \citealt{tbd-variability}, we assume that projectivity is a gradient property of utterance content: the more the speaker or author of the utterance is taken to be committed to the truth of an utterance content, the more projective the content is. To explore the projectivity of the prejacent, native speakers of American English were presented with naturally occurring NEAS and asked to rate the projectivity of the prejacent.\footnote{\label{f-git}The
materials, data and the R code for generating the figures and analyses of the experiments reported on in this paper are available at
\url{https://github.com/judith-tonhauser/evaluative-adjectives}.}

@@

\paragraph{Materials} Using the online interface of the EnTenTen corpus,\footnote{The EnTenTen 2012 corpus has 11,191,860,036 words
(\url{www.sketchengine.co.uk}, \citealt{ententen}).} we searched for NEASs that matched one of the strings in (\ref{string}), where ADJ was one of the following 10 evaluative adjectives that have been analyzed as presupposing the prejacent (e.g., \citealt{norrick78,karttunen-etal2014}): {\em stupid, smart, wise,
fortunate, lucky, brave, polite, mean, foolish} and {\em rude}.

@@

Each target stimulus was attributed to an author who was identified by name, as shown for the sample stimuli in (\ref{target1}). As shown in the `Question to participants' presented with each stimulus in (\ref{target1}), we used the `certain that' diagnostic for projectivity to assess whether participants took the author to be committed to the prejacent, i.e., whether the prejacent projects over negation. For other applications of the `certain that' diagnostic for projection see \citealt{tonhauser-salt26,djaerv-bacovcin-salt27,stevens-etal2017} and \citealt{tbd-variability}. In these `Questions to participants', the prejacent was realized as the finite complement clause of {\em certain}. The tense of the finite clause that realized the prejacent was determined by the temporal and aspectual properties of the
NEAS: it was past tense for past tense NEAS, as in (\ref{target1}a), and future tense for future tense NEAS, as in (\ref{target1}b); for non-past tense NEAS, the finite clause that realized the prejacent was realized in the non-past tense if the eventuality denoted by the prejacent was
stative, as in (\ref{target1}c), and a disjunction of a past tense and a future tense verb if the prejacent was eventive, as in (\ref{target1}d).

@@

\ex Shawn: Mr. Anderson --  Just discovered your
site on The 1939-40 New York World's Fair. It brought back a lot of
memories for me. Thanks for the time you spent in constructing this
site. I was not fortunate to visit the 1939-40 World's Fair but I
had an uncle who did.
\\ Question to participants: Is Shawn certain that he visited the 1939-40 World's Fair?

\ex Megan: For sure P1 will not be stupid to create a WiMAX netbook to allow YTL or AMAX customers to use.
\\ Question to participants: Is Megan certain that P1 will create a WiMAX netbook to allow YTL or AMAX customers to use?

\ex Frank: God offers Hope to Hispanics! In His pages are solutions to every immigration problem. God loves citizens and immigrants equally. His solutions are for all of us. They are practical. They work. He is not stupid to think so.
\\ Question to participants: Is Frank certain that God thinks that his solutions work?

\ex Anna: The flight attendants are not wise to invoke the specter
of a strike. \\ Question to participants: Is Anna certain that the
flight attendants invoked or will invoke the specter of a strike?

@@

\begin{figure}[h!]
\begin{center}
\fbox{\includegraphics[width=10cm]{figures/f-corpus-trial}}
\end{center}
\caption{A sample trial in Experiment 1}\label{f-corpus-trial}
\end{figure}

@@

\paragraph{Data exclusion} The responses from 6 participants who did not self-identify as native speakers of American English were excluded. 28 participants gave a rating higher than 3 to the control stimulus in (\ref{cntrl}a), for which we hypothesized that participants would not take the speaker to be committed to the relevant content, or a rating lower than 5 to the control stimulus in (\ref{cntrl}b), for which we hypothesized that participants would take the speaker to be committed to the relevant content. These responses suggest that these participants were not attending to the task or interpreted the task differently. We therefore also excluded the data from these 28 participants, leaving data from 226 participants (ages: 18-83; mean: 35).

@@

There were 26-32 certainty ratings for each of the 59 NEAS (mean: 28.5), except for the five NEASs that appeared on two lists, for which there were 52-58 certainty ratings each (mean: 54). We calculated the mean certainty rating of the prejacent of each NEAS: the lowest mean certainty rating was 1.2, the highest was 6.7 and the mean certainty rating overall was 3.2. Given that participants gave their ratings on a 7-point scale, with the lowest rating (1) indicating that the speaker was taken to not be certain about the relevant content and the highest rating (7) indicating that the speaker was taken to be certain about the relevant content, this mean certainty rating of 3.2 already suggests that the prejacent of naturally occurring NEAS is not highly projective. Figure \ref{f-corpus} shows the mean certainty rating of each NEAS by evaluative adjective. The distribution of mean certainty ratings again suggests that the prejacent of naturally occurring NEASs is projective, but not highly so, and that NEASs in which the prejacent does not project are well-attested in naturally occurring data. These findings provide empirical support for an analysis according to which the prejacent is not lexically specified as a presupposition.

@@

\includegraphics[width=.7\paperwidth]{../exp1-corpus-study/graphs/mean-response-by-item-and-adj}

\caption{Mean certainty ratings of 59 naturally occurring NEASs by evaluative adjective. Dotted error bars indicate bootstrapped 95\% confidence intervals.}\label{f-corpus}

@@

\ex God offers Hope to Hispanics! In His pages are solutions to every immigration problem. God loves citizens and immigrants equally. His solutions are for all of us. They are practical. They work. He is not stupid to think so. \hfill {\bf [6.3]}

\ex There is no chance a true large scale museum can be built. The federal government cannot take on the humongous legal liability for such a hazardous site. The Google founders are not stupid to take on that liability either. \hfill {\bf [1.9]}

@@

\ex Four months after her last Prolotherapy treatment  Tessie is still
doing great. But what would have happened if she was not
fortunate to be married to Joe? \hfill {\bf [6.4]}

\ex\label{fair}  Mr. Anderson  Just discovered your site on The 1939-40 New York World's Fair. It brought back a lot of memories for me. Thanks for the time you spent in constructing this site. I was not fortunate to visit the 1939-40 World's Fair but I had an uncle who did \hfill {\bf [1.2]}

@@

\ex Not even a 40 foot ladder could reach this roof  so I had to use a boom (bucket) lift. I got a 60' lift for this particular job  and it worked out nicely. I took the above photo while working in the lift. You can see the tiles. They look nice and neat in the photo  but up close  they were riddled with gaps. I spent a great deal of time sealing them. I was lucky to have level and relatively unobstructed ground. I was not lucky to have recent rains and a several ton machine to drive on the soft ground. \hfill {\bf [5.9]}

@@

\ex Alice: Good day. My husband and i were married for four years now but before that he already has a child with his ex gf. We are not lucky to have a child of our own. \hfill {\bf [1.4]}

@@

\begin{xlist} \ex Out east in St. Bernard Parish Chad Blanchard is
hoping he was not foolish to spend his savings on reopening
Charlie's restaurant -- leaving himself with just 15 dollar bills in his
back pocket. \\ \hspace*{.1cm} \hfill {\bf [5.4]}

@@

\ex Olmert is a dinosaur politician  he will exist for a long time in politics  and therefore will not be foolish to make the same mistake twice. \hfill {\bf [2.1]}

@@

\ex I think Mark Cuban was not smart to let a successful coach go in Avery Johnson. \hfill {\bf [6.7]}

@@

\ex Once you installed this free Notipage webpage monitoring software
then just make your first alert. It's worth mentioning here that the app
will not be smart to keep an eye on web pages that are only easy
to get to by logging in to a site or service.   \hfill {\bf [2.2]}

@@

In sum, our study of naturally occurring NEASs shows that the prejacent is not highly projective. These findings converge with those of \citet{tbd-variability}, who studied the projectivity of a variety of utterance contents and found that the prejacent of four (constructed) polar interrogative EASs with {\em stupid} was significantly less projective than the content of the clausal complement of the emotive predicate {\em be annoyed} and the cognitive predicate {\em know}. In the next section, we develop an analysis according to which the projectivity of the prejacent is not due to its lexical status as a presupposition but instead derived from the question that the utterance of the EAS is taken to address.

@@

\begin{exe}
\ex\label{ent} Two lexical entailments of unembedded evaluative adjective sentences `NP be{\sc .tense} Adj to VP'\footnote{Some EASs with {\em will} appear to not entail the prejacent: for example, some speakers do not judge (i) to entail that Johnson will take what he can get. We thank David Beaver (p.c.) for this point, which we sidestep here.
\begin{exe}
\exi{(i)} With more teams denying interest in Johnson, he will be smart
to take what he can get. \\ ({\em http://www.sportsworldreport.com/articles/28999/20140407/chris-johnson-rumors-ny-jets-release-mike-goodson-free-agent-signs-dallas-cowboys-demarco-murray-rams-falcons.htm})
\end{exe}}

@@

\ex Generalization: In VPing NP is/would be Adj

@@

\end{xlist}
\end{exe}
By (\ref{ent}), a past tense EAS like (\ref{f}) {\em Feynman was stupid to dance on the table} entails that, in dancing on the table, Feynman is/would be stupid (the generalization) and that Feynman danced on the table (the prejacent). Likewise, a present tense EAS like the non-negated variant of (\ref{stupid}b) {\em God is stupid to think that his solutions work} entails that, in thinking that his solutions work, God is/would be stupid (the generalization) and that God thinks that his solutions work (the prejacent). The generalization is timeless and attributes the property denoted by the evaluative adjective Adj to the referent of the subject NP relative to events of the type denoted by the VP. These events may, but need not be, actual: for instance, it does not follow from the generalization of (\ref{f}) that an event of Feynman dancing on the table took place.

In contrast to the generalization and the prejacent, we do not take the evaluation to be a lexical entailment of EASs (unlike, e.g., \citealt{barker02}). However, for unembedded EASs, the evaluation follows straightforwardly from the lexical entailments. For instance, in (\ref{f}), the evaluation that Feynman was stupid to dance on the table follows from the generalization, that in dancing on the table Feynman is/would be stupid, and the prejacent, that Feynman danced on the table. To preview the proposal: when an EAS is embedded under an entailment-canceling operator, it is not the case that both of the lexical entailments survive as commitments of the speaker. As a consequence, what follows from such EASs differs, thus capturing, as we show below, that the evaluation of such EASs depends on which content projects, i.e., is a commitment of the speaker.

The proposal in (\ref{ent}), according to which the prejacent and the generalization are lexical entailments, predicts that unembedded EASs are judged to be unacceptable if either entailment is false. The examples in (\ref{false}) show that that prediction is borne out. Consider (\ref{false}a), whose prejacent is false and whose generalization is true (under the assumption that anybody, including Kim, being born into poverty is unfortunate): this example is correctly predicted to be unacceptable because the prejacent is false. In (\ref{false}b), on the other hand, the prejacent is true and the generalization is false (under the assumption that it is not the case that anybody, including Sandy, being born into poverty is lucky). This sentence is correctly predicted to be judged to be unacceptable because the generalization is false.

@@

The generalization of an EAS involves the meaning of the (positive) evaluative adjective, whose meaning depends on a contextual standard (e.g., \citealt{kennedy2001}). Our examples in (\ref{false}) appealed to a contextual standard for {\em unfortunate} and {\em lucky} such that any reader would agree that somebody being born into poverty counts as unfortunate and doesn't count as lucky; more elaborately: the degree to which somebody being born into poverty is unfortunate is higher than the contextual standard for {\em unfortunate} and the degree to which somebody being born into poverty is lucky is lower than the contextual standard for {\em lucky}. What follows from the common ground, which we assume includes world knowledge, is that the generalization of (\ref{false}a), that in being born into poverty Kim is/would be unfortunate, is true and the generalization of (\ref{false}b), that in being born into poverty Sandy is/would be lucky, is false.

The common ground does not always determine whether the generalization of an EAS is true or false. Consider, for instance, the generalization that, in buying the Xbox 360 Elite, a particular individual $x$ is/would be stupid. Whether this generalization is true or false depends on $x$'s personal circumstances, such as how much money they have, whether they are addicted to gaming and shouldn't be tempted any further, or whether the Xbox is a present for somebody else. Common ground information does not suffice to identify whether the generalization is true or false; we refer to such generalizations as `neutral'. As a consequence, when a speaker utters the EAS in (\ref{xbox}), the generalization, that in buying the Xbox 360 Elite the speaker is/would be stupid, is new information that the speaker is committing to as true: the speaker informs the addressee that the degree to which them buying an Xbox 360 Elite is stupid is higher than the contextual standard of {\em stupid} (see also \citealt{barker02} for this point). For other speakers, this generalization may be false, in which case they could not truthfully utter (\ref{xbox}).

@@

\ex
\begin{xlist}
\exi{A:} The tickets for the show sold out really quickly! How did Sam get a ticket?

@@

\ex
\begin{xlist}
\exi{A:} Was Sam smart to buy a ticket for the show the day the tickets went on sale? The price would have gone down after a few days!

\exi{B:} Sam was smart to buy one the day they went on sale. The show sold out the day the tickets went on sale.

@@

\ex
\begin{xlist}
\exi{A:} Was Sam smart to buy a ticket for the show the day the tickets went on sale? The price would have gone down after a few days!

\exi{B:} Sam wasn't smart to buy one the day they went on sale. The price indeed went down after a few days.

@@

In this section, we argue that the information structure of an utterance of an EAS provides a cue to the Discourse Question addressed and, thereby, to the at-issueness of the prejacent.

@@

\begin{figure}[H]
\centering
